---
title: "Replication Code - Robustness Checks"
author: "Ebba Mark"
date: "`r Sys.Date()`"
output: html_document
---

# Overview

The following script conducts the various additional robustness checks reported
in the Supplementary Materials of the main manuscript including analysis of mine size heterogeneity, county-level dependence on coal mining, calculation of total employment loss numbers, exploration of persistent unemplyment rate effects, panel error corrected model, renewable energy investments. Each code block is labelled as it is in the Supplementary Materials to ease reading/searching.

The script produces the results reported in:
 - Supplementary Figures S6, S7
 - Supplementary Tables S12, S31-S37, S39, S40, S43-S50

The script draws on the following scripts and data sources:
Data Sources:
 - data/Econometrics_Final.xlsx: input data to econometric analysis
 - data/production_capacity/allcomp_cap_prod.RDS: production and state productive capacity data as compiled in prod_cap_cleaning.R
- data/FIPSModificationsVA.xlsx: crosswalk between selected Virginia fips codes that differ between the Bureau of Economic Analysis and Census Bureau
- data/cc_clusters_251.xlsx: dataset documenting the "type" of each county as calculated in main_typology.Rmd. This is an output of main_typology.Rmd
 - data/county_adjacency.txt: county adjacency matrix
 - data/industry-titles.xlsx: NAICS industry codes look-up file
 - data/qcew_compiled_raw_2000_2022.RDS: compiled data from US Census Bureau's Quarterly Census on Employment and Wages used to calculate sector-level employment impacts

 
Scripts:
- code/dicts.R: provides fixest and other dictionaries for regression output and summary statistics tables
- code/useful_functions.R: includes various functions called throughout the script. Mainly these are functions that make certain regression output compatible with summary table functions and coefficient plot functions. This also outlines the Louisiana counties that have missing values in our main dataset to ensure that these are excluded in the spatial neighbor matrix generated in main_econometrics.Rmd


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Libraries
```{r cars}

library(tidyverse)
library(readxl)
library(here)
library(openxlsx)
library(gdata)
library(janitor)
library(tidycensus)
library(zoo)
library(splm)
library(spdep)
library(multcomp)
library(modelsummary)
library(stargazer)
library(kableExtra)
library(conflicted)
library(fixest)
library(plm)
library(zoo)
conflict_prefer_all("dplyr", quiet = TRUE)
setwd(here("replication_code"))

```

# Data

```{r}

# Production and productive capacity data cleaned in prod_cap_cleaning.R
# This dataset contains all variables from Econometrics_Final.xlsx with additional production and productive capacity data as cleaned in prod_cap_cleaning.R
allcomp <- readRDS("data/production_capacity/allcomp_cap_prod.RDS")

```


```{r cars}
# Unmodified lookup table to adjust FIPS codes between various standards
bea_fips_mods <- read_excel("data/FIPSModificationsVA.xlsx", skip = 1, col_types = c("text", "text","text","text"))

# Create subset of coal counties (CC) only (with active mines at some point)
cclist <- unique(allcomp$fips[which(allcomp$active_mines != 0)])
allcomp_cc <- subset(allcomp, fips %in% cclist)

# Dataset including the "type" of county as found in the Typology work (Typology Work_New.Rmd)
# Merged with CC dataset
cc_cluster <- read_excel("data/cc_clusters_251.xlsx")
allcomp_cc_types <- merge(allcomp_cc, cc_cluster, by = "fips", all.x = TRUE)

# Load required functions and dictionaries
source("code/useful_functions.R")
source("code/dicts.R")

# Create adjacency matrix for spatial model
##############################################################
# Import adjacency matrix from US Census Bureau: 
# https://www.census.gov/programs-surveys/geography/library/reference/county-adjacency-file.html
xmat1 <- read.csv("data/county_adjacency.txt", sep="\t", stringsAsFactors = FALSE, header = FALSE)

# Retain only columns with FIPS codes of each county (V2) and its neighbors (V4)
xmat1 <- xmat1[,c("V2","V4")]

# Replace NA values in V2 such that each row is a pair of neighbors
xmat1$V2 <- na.locf(xmat1$V2)

# Convert from integer to character fips code for appropriate matching
xmat1$V2 <- lapply(xmat1$V2, function(x) sapply(x, fips_format))
xmat1$V4 <- lapply(xmat1$V4, function(x) sapply(x, fips_format))

# Create lookup table to convert VA FIPS codes
getfips <- bea_fips_mods$`BEA FIPS`
names(getfips) <- bea_fips_mods$FIPS

xmat1[xmat1 == "46113"] <- "46102"
xmat1[xmat1 == "51515"] <- "51019"
xmat1$V2 <- lapply(xmat1$V2, function(x) ifelse(x %in% bea_fips_mods$FIPS, getfips[x], x))
xmat1$V4 <- lapply(xmat1$V4, function(x) ifelse(x %in% bea_fips_mods$FIPS, getfips[x], x))

# Removes Alaska, Hawaii, DC, PR, Guam, American Samoa
xmat1 <- subset(xmat1, substr(V2, 1, 2) != "60" & 
                  substr(V2, 1, 2) != "66" &
                  substr(V2, 1, 2) != "69" &
                  substr(V2, 1, 2) != "72" &
                  substr(V2, 1, 2) != "78" &
                  substr(V2, 1, 2) != "15" &
                  substr(V2, 1, 2) != "02")

LA_list <- c(LA_list_missing, "11001")
xmat1 <- subset(xmat1, !(V2 %in% LA_list) & !(V4 %in% LA_list))

length(unique(xmat1$V2))

# Unnest list elements for easier manipulation
xmat1 <- unnest(xmat1)
# Create a list of each unique FIPS code for matching
fipslist <- unique(xmat1$V2)

# Subset dataframe to only include FIPS present in the distance matrix
allcomp_nomissing <- subset(allcomp, fips %in% fipslist)
#allcomp_nomissing <- subset(allcomp_nomissing, fips != "51770")
allcomp_full <- allcomp_nomissing %>%
  arrange(fips) %>%
  select(fips,year,everything())

xmatfips <- unique(xmat1$V2)

# Create an empty (all cells = 0) n x n distance matrix with n = no of FIPS codes/counties
fmat <- matrix(data=0, nrow = length(xmatfips), ncol = length(xmatfips), dimnames = list(xmatfips,xmatfips))

# Iterate through xmatfips, populating matrix with 1 if two counties are neighbors
# Census bureau lists counties as neighbors of itself so the loop will fill cell 
# with 0 for row-pair that lists a county as a neighbor of itself
for(i in 1:nrow(xmat1)){
  a = as.character(xmat1$V2[i])
  b = as.character(xmat1$V4[i])
  if(identical(a,b)){fmat[a,b] <- 0}else{fmat[a,b] <- 1}
}

# Row standardises the distance matrix
fmat <- fmat/rowSums(fmat)
sum(is.na(fmat))
dim(fmat)

# Creates listw object for use in splm package
fmatlw <- mat2listw(fmat, style = "W")

# Also a test for errors
testfmatcdg <- listw2dgCMatrix(fmatlw)

# Sanity checks
### Ensure panel is balanced
is.pbalanced(allcomp_full)
### No NAs
sum(is.na(fmatlw))
```


## Heterogeneity in Mine Size: Production and Capacity

```{r cars}

FE_diffuer <- as.formula("diff_uer ~ mines_diff + lag_diff + lag_diff2 + diff_log_realgdp_pc | fips + year")
FE_prod_orig <- as.formula("diff_uer ~ prod_diff + lag_prod_diff + lag_prod_diff2 + diff_log_realgdp_pc | fips + year")
FE_prod_cap2 <- as.formula("diff_uer ~ diff_prod_cap2 + l1_diff_prod_cap2 + l2_diff_prod_cap2 + diff_log_realgdp_pc | fips + year")

main <- feols(FE_diffuer, allcomp, se = 'twoway')
main_prod_orig <- feols(FE_prod_orig, allcomp, se = 'twoway')
main_cap2 <- feols(FE_prod_cap2, allcomp, se = 'twoway')
modelsummary(list(main, main_prod_orig, main_cap2), stars = TRUE)

allcomp_full$diff_log_realgdp_pc[which(allcomp_full$fips == "08014" & allcomp_full$year == 2002)] <- 0
allcomp_full$diff_log_realgdp[which(allcomp_full$fips == "08014" & allcomp_full$year == 2002)] <- 0
allcomp_full$diff_log_pop[which(allcomp_full$fips == "08014" & allcomp_full$year == 2002)] <- 0

fmdiff_prod <- diff_uer ~ prod_diff + lag_prod_diff + lag_prod_diff2 + diff_log_realgdp_pc
fmdiff_prodcap2 <- diff_uer ~ diff_prod_cap2 + l1_diff_prod_cap2 + l2_diff_prod_cap2 + diff_log_realgdp_pc

sp_err_lag_prod <- spml(fmdiff_prod, data = allcomp_full, index = NULL,  listw = fmatlw, 
                         lag = TRUE, na.action = na.fail, spatial.error = "b",
                         model = "within", effect = "twoways", quiet = FALSE)

sp_err_lag_cap2 <- spml(fmdiff_prodcap2, data = allcomp_full, index = NULL,  listw = fmatlw, 
                       lag = TRUE, na.action = na.fail, spatial.error = "b",
                       model = "within", effect = "twoways", quiet = FALSE)

allcomp_pdf <- pdata.frame(allcomp_full, index = c("fips", "year"))
allcomp_pdf$sl_prod_diff <- slag(allcomp_pdf$prod_diff, fmatlw)
allcomp_pdf$sl_lag_prod_diff <- slag(allcomp_pdf$lag_prod_diff, fmatlw)
allcomp_pdf$sl_lag_prod_diff2 <- slag(allcomp_pdf$lag_prod_diff2, fmatlw)

allcomp_pdf$sl_diff_prod_cap2 <- slag(allcomp_pdf$diff_prod_cap2, fmatlw)
allcomp_pdf$sl_l1_diff_prod_cap2 <- slag(allcomp_pdf$l1_diff_prod_cap2, fmatlw)
allcomp_pdf$sl_l2_diff_prod_cap2 <- slag(allcomp_pdf$l2_diff_prod_cap2, fmatlw)

fmdiff_prod_spl <-  diff_uer ~ prod_diff + lag_prod_diff + lag_prod_diff2 + diff_log_realgdp_pc + sl_prod_diff + sl_lag_prod_diff + sl_lag_prod_diff2
fmdiff_cap2_spl2 <-  diff_uer ~ diff_prod_cap2 + l1_diff_prod_cap2 + l2_diff_prod_cap2 + diff_log_realgdp_pc + sl_diff_prod_cap2 + sl_l1_diff_prod_cap2 + sl_l2_diff_prod_cap2

# run model
durbin_error_prod <- spml(fmdiff_prod_spl, data = allcomp_pdf, listw = fmatlw, model="within", effect = "twoways", quiet = FALSE, spatial.error = "b")
summary(durbin_error_prod)

durbin_error_cap2 <- spml(fmdiff_cap2_spl2, data = allcomp_pdf, listw = fmatlw, model="within", effect = "twoways", quiet = FALSE, spatial.error = "b")
summary(durbin_error_cap2)

sparse.W <- listw2dgCMatrix(fmatlw)
time <- length(unique(allcomp_full$year))
s.lwcounties <- kronecker(Matrix::Diagonal(time), sparse.W)
trMatc <- spatialreg::trW(s.lwcounties, type="mult")
imperrlag_prod <- impacts(sp_err_lag_prod, tr = trMatc, R = 200)
imperrlag_cap2 <- impacts(sp_err_lag_cap2, tr = trMatc, R = 200)

names_prod <- c("Production_{i,t}", "Production_{i,t-1}", "Production_{i,t-2}", "(log) Real GDPPC")
names_cap2 <- c("Capacity*_{i,t}", "Capacity*_{i,t-1}", "Capacity*_{i,t-2}", "(log) Real GDPPC")
names_durbin_prod <- c("Production_{i,t}", "Production_{i,t-1}", "Production_{i,t-2}", "(log) Real GDPPC", "Production_{-i,t}", "Production_{-i,t-1}", "Production_{-i,t-2}")
names_durbin_cap2 <- c("Capacity*_{i,t}", "Capacity*_{i,t-1}", "Capacity*_{i,t-2}", "(log) Real GDPPC", "Capacity*_{-i,t}", "Capacity*_{-i,t-1}", "Capacity*_{-i,t-2}")


# SARAR Results
sarar_tbl <-cbind(spat_output_rob(imperrlag_prod), 
                    spat_output_rob(imperrlag_cap2))


###############################################################################
###############################################################################
#### SUPPLEMENTARY TABLE S33
sarar_tbl[1:5] %>% 
  tibble %>% 
  mutate(var = case_when(var == "prod_diff" ~ "Production_{i,t}",
                         var == "lag_prod_diff" ~ "Production_{i,t-1}",
                         var == "lag_prod_diff2" ~ "Production_{i,t-2}",
                         var == "diff_log_realgdp_pc" ~ "(log) Real GDPPC")) %>% 
  left_join(sum_tbl(durbin_error_prod, names_durbin_prod, TRUE), ., by = c("var", "measure")) %>% 
  left_join(., sum_tbl(main_prod_orig, names_prod, FALSE), by = c("var", "measure")) %>% 
  relocate(var, measure, estimate.y, estimate.x, Direct, Indirect, Total) %>% 
  mutate(var = ifelse(row_number()%%2, var, "")) %>% 
  select(-measure) %>% 
  kable(., booktabs=TRUE, format = "latex") %>% 
  kable_styling(position="center")

###############################################################################
###############################################################################


###############################################################################
###############################################################################
#### SUPPLEMENTARY TABLE S34
sarar_tbl[6:10] %>% 
  tibble %>% 
  mutate(var = case_when(var == "diff_prod_cap2" ~ "Capacity*_{i,t}",
                         var == "l1_diff_prod_cap2" ~ "Capacity*_{i,t-1}",
                         var == "l2_diff_prod_cap2" ~ "Capacity*_{i,t-2}",
                         var == "diff_log_realgdp_pc" ~ "(log) Real GDPPC")) %>% 
  left_join(sum_tbl(durbin_error_cap2, names_durbin_cap2, TRUE), ., by = c("var", "measure")) %>% 
  left_join(sum_tbl(main_cap2, names_cap2, FALSE), by = c("var", "measure")) %>% 
  relocate(var, measure, estimate.y, estimate.x, Direct, Indirect, Total) %>% 
  mutate(var = ifelse(row_number()%%2, var, "")) %>% 
  select(-measure) %>% 
  kable(., booktabs=TRUE, format = "latex") %>% 
  kable_styling(position="center")

###############################################################################
###############################################################################

```



## Underground versus Surface Coal Mines

```{r cars}

FE_diffuer <- as.formula("diff_uer ~ mines_diff + lag_diff + lag_diff2 + diff_log_realgdp_pc | fips + year")
FE_diff_surface <- as.formula("diff_uer ~ diff_surface_active_n + l1_diff_surface_active_n + l2_diff_surface_active_n + diff_log_realgdp_pc | fips + year")
FE_diff_underground <-as.formula("diff_uer ~ diff_underground_active_n + l1_diff_underground_active_n + l2_diff_underground_active_n + diff_log_realgdp_pc | fips + year")

main <- feols(FE_diffuer, allcomp, se = 'twoway')
main_surface <- feols(FE_diff_surface, allcomp, se = 'twoway')
main_underground <- feols(FE_diff_underground, allcomp, se = 'twoway')
modelsummary(list(main, main_surface, main_underground), stars = TRUE)
  
############ SPATIAL ########
allcomp_full$diff_log_realgdp_pc[which(allcomp_full$fips == "08014" & allcomp_full$year == 2002)] <- 0
allcomp_full$diff_log_realgdp[which(allcomp_full$fips == "08014" & allcomp_full$year == 2002)] <- 0
allcomp_full$diff_log_pop[which(allcomp_full$fips == "08014" & allcomp_full$year == 2002)] <- 0


fmdiff_surface <- diff_uer ~ diff_surface_active_n + l1_diff_surface_active_n + l2_diff_surface_active_n + diff_log_realgdp_pc
fmdiff_underground <- diff_uer ~ diff_underground_active_n + l1_diff_underground_active_n + l2_diff_underground_active_n + diff_log_realgdp_pc

sp_err_lag_surface <- spml(fmdiff_surface, data = allcomp_full, index = NULL,  listw = fmatlw, 
                        lag = TRUE, na.action = na.fail, spatial.error = "b",
                        model = "within", effect = "twoways", quiet = FALSE)

sp_err_lag_underground <- spml(fmdiff_underground, data = allcomp_full, index = NULL,  listw = fmatlw, 
                       lag = TRUE, na.action = na.fail, spatial.error = "b",
                       model = "within", effect = "twoways", quiet = FALSE)

allcomp_pdf$sl_diff_surface_active_n <- slag(allcomp_pdf$diff_surface_active_n, fmatlw)
allcomp_pdf$sl_l1_diff_surface_active_n <- slag(allcomp_pdf$l1_diff_surface_active_n, fmatlw)
allcomp_pdf$sl_l2_diff_surface_active_n <- slag(allcomp_pdf$l2_diff_surface_active_n, fmatlw)

allcomp_pdf$sl_diff_underground_active_n <- slag(allcomp_pdf$diff_underground_active_n, fmatlw)
allcomp_pdf$sl_l1_diff_underground_active_n <- slag(allcomp_pdf$l1_diff_underground_active_n, fmatlw)
allcomp_pdf$sl_l2_diff_underground_active_n <- slag(allcomp_pdf$l2_diff_underground_active_n, fmatlw)

fmdiff_surface_spl <-  diff_uer ~ diff_surface_active_n + l1_diff_surface_active_n + l2_diff_surface_active_n + diff_log_realgdp_pc + sl_diff_surface_active_n + sl_l1_diff_surface_active_n + sl_l2_diff_surface_active_n
fmdiff_underground_spl <-  diff_uer ~ diff_underground_active_n + l1_diff_underground_active_n + l2_diff_underground_active_n + diff_log_realgdp_pc + sl_diff_underground_active_n + sl_l1_diff_underground_active_n + sl_l2_diff_underground_active_n


# run model
durbin_error_surface <- spml(fmdiff_surface_spl, data = allcomp_pdf, listw = fmatlw, model="within", effect = "twoways", quiet = FALSE, spatial.error = "b")
summary(durbin_error_surface)

durbin_error_underground <- spml(fmdiff_underground_spl, data = allcomp_pdf, listw = fmatlw, model="within", effect = "twoways", quiet = FALSE, spatial.error = "b")
summary(durbin_error_underground)


sparse.W <- listw2dgCMatrix(fmatlw)
time <- length(unique(allcomp_full$year))
s.lwcounties <- kronecker(Matrix::Diagonal(time), sparse.W)
trMatc <- spatialreg::trW(s.lwcounties, type="mult")
#implag <- impacts(sp_lag_prod, tr = trMatc, R = 200)
imperrlag_surface <- impacts(sp_err_lag_surface, tr = trMatc, R = 200)
imperrlag_underground <- impacts(sp_err_lag_underground, tr = trMatc, R = 200)


summary(imperrlag_surface, zstats=TRUE, short=TRUE)
summary(imperrlag_underground, zstats=TRUE, short=TRUE)

summary(durbin_error_surface)
summary(durbin_error_underground)


names_surface <- c("Diff Active Surface Mines_{i,t}", "Diff Active Surface Mines_{i,t-1}", "Diff Active Surface Mines_{i,t-2}", "Diff (log) Real GDPPC")
names_durbin_surface <- c("Diff Active Surface Mines_{i,t}", "Diff Active Surface Mines_{i,t-1}", "Diff Active Surface Mines_{i,t-2}", "Diff (log) Real GDPPC", "Diff Active Surface Mines_{-i,t}", "Diff Active Surface Mines_{-i,t-1}", "Diff Active Surface Mines_{-i,t-2}")
names_underground <- c("Diff Active Underground Mines_{i,t}", "Diff Active Underground Mines_{i,t-1}", "Diff Active Underground Mines_{i,t-2}", "Diff (log) Real GDPPC")
names_durbin_underground <- c("Diff Active Underground Mines_{i,t}", "Diff Active Underground Mines_{i,t-1}", "Diff Active Underground Mines_{i,t-2}", "Diff (log) Real GDPPC", "Diff Active Underground Mines_{-i,t}", "Diff Active Underground Mines_{-i,t-1}", "Diff Active Underground Mines_{-i,t-2}")


###############################################################################
###############################################################################
#### SUPPLEMENTARY TABLE S31
sarar_tbl <-cbind(spat_output_rob(imperrlag_surface), 
                  spat_output_rob(imperrlag_underground))
                  
sarar_tbl[1:5] %>% 
  tibble %>% 
  mutate(var = case_when(var == "diff_surface_active_n" ~ "Diff Active Surface Mines_{i,t}",
                         var == "l1_diff_surface_active_n" ~ "Diff Active Surface Mines_{i,t-1}",
                         var == "l2_diff_surface_active_n" ~ "Diff Active Surface Mines_{i,t-2}",
                         var == "diff_log_realgdp_pc" ~ "Diff (log) Real GDPPC")) %>% 
  left_join(sum_tbl(durbin_error_surface, names_durbin_surface, TRUE), ., by = c("var", "measure")) %>% 
  left_join(., sum_tbl(main_surface, names_surface, FALSE), by = c("var", "measure")) %>% 
  relocate(var, measure, estimate.y, estimate.x, Direct, Indirect, Total) %>% 
  mutate(var = ifelse(row_number()%%2, var, "")) %>% 
  select(-measure) %>% 
  kable(., booktabs=TRUE, format = "latex") %>% 
  kable_styling(position="center")
###############################################################################
###############################################################################


###############################################################################
###############################################################################
#### SUPPLEMENTARY TABLE S32
sarar_tbl[6:10] %>% 
  tibble %>% 
  mutate(var = case_when(var == "diff_underground_active_n" ~ "Diff Active Underground Mines_{i,t}",
                         var == "l1_diff_underground_active_n" ~ "Diff Active Underground Mines_{i,t-1}",
                         var == "l2_diff_underground_active_n" ~ "Diff Active Underground Mines_{i,t-2}",
                         var == "diff_log_realgdp_pc" ~ "Diff (log) Real GDPPC")) %>% 
  left_join(sum_tbl(durbin_error_underground, names_durbin_underground, TRUE), ., by = c("var", "measure")) %>% 
  left_join(., sum_tbl(main_underground, names_underground, FALSE), by = c("var", "measure")) %>% 
  relocate(var, measure, estimate.y, estimate.x, Direct, Indirect, Total) %>% 
  mutate(var = ifelse(row_number()%%2, var, "")) %>% 
  select(-measure) %>% 
  kable(., booktabs=TRUE, format = "latex") %>% 
  kable_styling(position="center")
###############################################################################
###############################################################################

```

## Effect of Change in Active Mines on Sector-level Employment
```{r}
### Employment numbers #####
# This data is pulled from QCEW: Source: https://www.bls.gov/cew/downloadable-data-files.htm.- CSVs Single Files: Annual Averages
# Industry codes provided by QCEW BLS: https://www.bls.gov/cew/classifications/industry/industry-titles.htm

# Each individual file is VERY large and therefore we have compiled this work separately into "qcew_compiled_raw_2000_2022.RDS" with the following code provided the data is downloaded and unzipped

# df_list <- list()
# for(y in 1990:2022){
#   print(y)
#   df_list[[as.character(y)]] <- read.csv(here(paste0(as.character(y), ".annual.singlefile.csv"))) %>%
#     tibble %>%
#     mutate(year = y) %>%
#     left_join(., ind_codes, by = "industry_code") 
# }

#saveRDS(df_list, here("data/temp/qcew_compiled_raw_2000_2022.RDS"))

ind_codes <- read_excel("data/industry-titles.xlsx")
temp_test <- readRDS("data/qcew_compiled_raw_2000_2022.RDS")

temp <- temp_test %>% 
  filter(substr(area_fips, 3,5) != "000" & substr(area_fips, 3,5) != "999") %>%  
  mutate(fips_state = substr(area_fips, 1,2)) %>% 
  rename(fips = area_fips) %>% 
  filter(!(fips_state %in% c("72","78", "C1", "C2", "C3", "C4", "CS"))) %>% 
  mutate(fips = ifelse(fips %in% names(getfips), unname(getfips[fips]), fips)) %>% 
  filter(!(fips %in% c("51560", "51515")) & !(fips == "46113" & year == 2015)) %>% 
  mutate(fips = ifelse(fips == "46113", "46102", fips)) %>%
  # Agglevel codes: https://www.bls.gov/cew/classifications/aggregation/agg-level-titles.htm  
  #       only "total industry" has multiple agg level codes - 70 is the correct one for county totals
  filter(!(industry_code == 10 & agglvl_code != 70)) %>% 
  select(fips, year, industry_code, industry_title, annual_avg_estabs, annual_avg_emplvl, total_annual_wages, avg_annual_pay) %>% 
  # Any counties that have multiple observations DO NOT HAVE A TOTAL "OWN-CODE = 0" or TOTAL GOVERNMENT "OWN-CODE = 8" record - therefore we group by fips, year, industry_code and sum total
  group_by(fips, year, industry_code, industry_title) %>% 
  summarise(across(c(annual_avg_estabs, annual_avg_emplvl, total_annual_wages, avg_annual_pay), ~sum(., na.rm = TRUE))) %>% 
  ungroup 

# There are 12 exceptions ot the above filtering of industrycode == 10 - 0 reported for total but there are lower level estimates. The below creates this supplement
temp_supp <- temp_test %>% 
  filter(substr(area_fips, 3,5) != "000" & substr(area_fips, 3,5) != "999") %>%  
  mutate(fips_state = substr(area_fips, 1,2)) %>% 
  rename(fips = area_fips) %>% 
  filter(!(fips_state %in% c("72","78", "C1", "C2", "C3", "C4", "CS"))) %>% 
  mutate(fips = ifelse(fips %in% names(getfips), unname(getfips[fips]), fips)) %>% 
  filter(!(fips %in% c("51560", "51515")) & !(fips == "46113" & year == 2015)) %>% 
  mutate(fips = ifelse(fips == "46113", "46102", fips)) %>%
  # Agglevel codes: https://www.bls.gov/cew/classifications/aggregation/agg-level-titles.htm  
  #       only "total industry" has multiple agg level codes - 70 is the correct one for county totals
  group_by(fips, year) %>% 
  filter(industry_code == "10" & any(agglvl_code == "70" & annual_avg_emplvl == 0) & fips %in% unique(allcomp$fips)) %>% 
  ungroup %>% 
  select(fips, year, industry_code, industry_title, annual_avg_estabs, annual_avg_emplvl, total_annual_wages, avg_annual_pay) %>% 
  # Any counties that have multiple observations DO NOT HAVE A TOTAL "OWN-CODE = 0" or TOTAL GOVERNMENT "OWN-CODE = 8" record - therefore we group by fips, year, industry_code and sum total
  group_by(fips, year, industry_code, industry_title) %>% 
  summarise(across(c(annual_avg_estabs, annual_avg_emplvl, total_annual_wages, avg_annual_pay), ~sum(., na.rm = TRUE))) %>% 
  ungroup

emp_df <- temp %>% 
  filter(!(industry_code == "10" & annual_avg_emplvl == 0)) %>% 
  rbind(temp_supp) %>% 
 # "42352" ~ Coal and other mineral and ore merchant wholesalers
 # "213113" ~ Support activities for coal mining
 # "2121" ~ Coal mining
 # "221112" Fossil fuel electric power generation
  filter(nchar(industry_code) <= 2 | industry_code %in% c("42352", "213113", "2121", "221112")) %>% 
  select(fips, year, industry_code, annual_avg_emplvl) %>% 
  mutate(nc = nchar(industry_code)) %>% 
  arrange(nc) %>% 
  select(-nc) %>% 
  pivot_wider(id_cols = c("fips", "year"), names_from = industry_code, values_from = annual_avg_emplvl, names_prefix = "emp_") %>% 
  mutate(across(where(is.numeric), ~ifelse(is.na(.), 0, .))) %>% 
  mutate(emp_coal = emp_2121 + emp_213113,
         emp_coal_sales = emp_coal + emp_42352,
         emp_coal_ff_gen = emp_coal_sales + emp_221112,
         emp_non_coal = emp_10 - emp_coal_sales) %>% 
  select(-c(emp_42352, emp_213113, emp_2121, emp_221112, emp_99)) %>% 
  complete(fips, year) %>% 
  mutate(across(contains("emp"), ~./1000)) %>% 
  mutate(across(contains("emp"), .fns = list(log = ~log(. + 1)), .names = "{.fn}_{.col}")) %>% 
  group_by(fips) %>% 
  mutate(across(contains("emp"), .fns = list(diff = ~c(NA,diff(.))), .names = "{.fn}_{.col}")) %>% 
  ungroup %>% 
  mutate(coal_share_emp = emp_coal/emp_10,
         coal_sales_share_emp = emp_coal_sales/emp_10) %>% 
  group_by(fips) %>% 
  mutate(across(c(coal_share_emp, coal_sales_share_emp), .fns = list(l1 = ~lag(.x, 1), l2 = ~lag(.x, 2)), .names = "{.fn}_{.col}")) %>% 
            ungroup

is.pbalanced(emp_df)

allcomp_emp <- read_excel("data/Econometrics_Final.xlsx") %>% 
  left_join(., emp_df, by = c("fips", "year"))

# Also create a variable for the coal share of total employment
deps <- emp_df %>% select(-c(fips, year)) %>% names 

coal_emp_mods <- feols(.[deps[grepl("coal", deps)]] ~ mines_diff + lag_diff + lag_diff2 + diff_log_pop + diff_log_realgdp | fips + year, allcomp_emp, se = 'twoway')

other_emp_mods <- feols(.[deps[!grepl("coal", deps)]] ~ mines_diff + lag_diff + lag_diff2 + diff_log_pop + diff_log_realgdp | fips + year, allcomp_emp, se = 'twoway')

for(tt in list("emp_coal$", "emp_coal_sales", "emp_coal_ff_gen", "emp_non_coal")){
  coal_emp_mods[lhs = tt] %>% etable(title = tt) %>% print
}


################################################################################
# Controlling appropriately for population and log_realgdp
# Also create a variable for the coal share of total employment

deps <- emp_df %>% select(contains("diff_log_emp")) %>% names 

coal_emp_mods <- feols(.[deps[grepl("coal", deps)]] ~ mines_diff + lag_diff + lag_diff2 + diff_log_pop + diff_log_realgdp | fips + year, allcomp_emp, se = 'twoway')

other_emp_mods <- feols(.[deps[!grepl("coal", deps)]] ~ mines_diff + lag_diff + lag_diff2 + diff_log_pop + diff_log_realgdp | fips + year, allcomp_emp, se = 'twoway')


###############################################################################
###############################################################################
#### SUPPLEMENTARY TABLE S39
coal_emp_mods[lhs = c("diff_log_emp_coal", "diff_log_emp_coal_sales", "diff_log_emp_coal_ff_gen", "diff_log_emp_non_coal")] %>% etable(title = "Change in (log) Employment Levels", tex = TRUE) %>% print
###############################################################################
###############################################################################


###############################################################################
###############################################################################
#### SUPPLEMENTARY TABLE S40
other_emp_mods[lhs = c("diff_log_emp_10", "diff_log_emp_23", "diff_log_emp_72", "diff_log_emp_21", "diff_log_emp_55", "diff_log_emp_61")] %>% etable(title = "Change in (log) Employment Levels (Secondary Sectors)", tex = TRUE) %>% print
###############################################################################
###############################################################################

```

## Heterogeneity in Share of County-Level Employment in Coal Mining
```{r}
#### CONTROLLING FOR SHARE IN EMPLOYMENT ######
temp_emp_interpol <- allcomp_emp %>% 
  group_by(state.x, year) %>% 
  mutate(lab_prod_state = sum(emp_coal, .na.rm = TRUE)/sum(active_mines, na.rm = TRUE)) %>% 
  ungroup %>%
  group_by(fips, year) %>%
  mutate(lab_prod_county = emp_coal/active_mines) %>% 
  #select(fips, year, emp_coal, active_mines, lab_prod_state, lab_prod_county) %>% 
  group_by(fips) %>% 
  mutate(lab_prod_county = ifelse(lab_prod_county == 0, NA, lab_prod_county),
         lab_prod_county_interpol = na.approx(lab_prod_county, na.rm=FALSE), 
         lab_prod_county_interpol = ifelse(is.infinite(lab_prod_county_interpol), NA, lab_prod_county_interpol),
         lab_prod_county_mean = mean(lab_prod_county, na.rm = TRUE),
         lab_prod_county_mean = ifelse(is.nan(lab_prod_county_mean) | is.infinite(lab_prod_county_mean), NA, lab_prod_county_mean)) %>% 
  fill(lab_prod_county_interpol, .direction = "updown") %>% 
  mutate(lab_prod_county_interpol = ifelse(is.na(lab_prod_county_interpol), lab_prod_state, lab_prod_county_interpol),
         lab_prod_county_mean = ifelse(is.na(lab_prod_county_mean), lab_prod_state, lab_prod_county_mean)) %>% 
  ungroup %>%
  mutate(coal_share_emp_interpol = ifelse(coal_share_emp == 0, (active_mines*lab_prod_county_interpol)/emp_10, coal_share_emp),
         coal_share_emp_mean = ifelse(coal_share_emp == 0, (active_mines*lab_prod_county_mean)/emp_10, coal_share_emp),
         coal_share_emp_interpol = ifelse(is.na(coal_share_emp_interpol), 0, coal_share_emp_interpol),
         coal_share_emp_mean = ifelse(is.na(coal_share_emp_mean), 0, coal_share_emp_mean),
         across(c(coal_share_emp, coal_share_emp_interpol, coal_share_emp_mean), ~case_when(. <= 0.1 ~ "low",
                                       . > 0.1 & . <= 0.2 ~ "medium",
                                       . > 0.2 ~ "high"), .names = "{.col}_discrete"), 
         across(contains("discrete"), ~factor(., levels = c("low", "medium", "high"))))

FE_diffuer_main <- feols(diff_uer ~ mines_diff + lag_diff + lag_diff2 + diff_log_realgdp_pc | fips + year, allcomp_emp, se = "twoway")
control_share_raw <- "diff_uer ~ mines_diff + lag_diff + lag_diff2 + diff_log_realgdp_pc + coal_share_emp | fips + year"
share_forms <- list(control_share_raw,
                    gsub("coal_share_emp", "coal_share_emp_interpol", control_share_raw),
                    gsub("coal_share_emp", "coal_share_emp_mean", control_share_raw),
                    "diff_uer ~ coal_share_emp_discrete*mines_diff + coal_share_emp_discrete*lag_diff + coal_share_emp_discrete*lag_diff2 + diff_log_realgdp_pc | fips + year",
                    "diff_uer ~ coal_share_emp_interpol_discrete*mines_diff + coal_share_emp_interpol_discrete*lag_diff + coal_share_emp_interpol_discrete*lag_diff2 + diff_log_realgdp_pc | fips + year",
                    "diff_uer ~ coal_share_emp_mean_discrete*mines_diff + coal_share_emp_mean_discrete*lag_diff + coal_share_emp_mean_discrete*lag_diff2 + diff_log_realgdp_pc | fips + year")


share_results <- list(FE_diffuer_main)
for(el in share_forms){
  share_results <- c(share_results, list(feols(as.formula(el), data = temp_emp_interpol, se = "twoway")))
}

share_results[7]


###############################################################################
###############################################################################
#### SUPPLEMENTARY TABLE S35

# Orders by variable for coal share of employment used
share_results[c(1,2,5,3,6,4,7)] %>% etable(tex = TRUE)
###############################################################################
###############################################################################

#### Linear hypothesis tests

glht_contemp <- list()
contemp_tests <- c()
glht_persistent <- list()
persistence_tests <- c()
for(k in share_results[c(1,2,5,3,6,4,7)]){
  k$coefficients
  glht_low <- glht(k, linfct = "mines_diff = 0")
  # Contemporaneous tests
  tests_med <- k$coefficients %>% purrr::keep(grepl("medium:mines_diff", names(.), fixed = TRUE)) %>% names
  tests_high <- k$coefficients %>% purrr::keep(grepl("high:mines_diff", names(.), fixed = TRUE)) %>% names
  if(length(tests_med) != 0 & length(tests_high) != 0){
    hyp_test_contemp_med <- paste0("mines_diff + ", tests_med, " = 0")
    glht_med <- glht(k, linfct = hyp_test_contemp_med)
    hyp_test_contemp_high <- paste0("mines_diff + ", tests_high, " = 0")
    glht_high <- glht(k, linfct = hyp_test_contemp_high)
    glht_contemp <- c(glht_contemp, list(glht_low), list(glht_med), list(glht_high))
    contemp_tests <- c(contemp_tests, hyp_test_contemp_med, hyp_test_contemp_high)
  }else{
    glht_contemp <- c(glht_contemp, list(glht_low))
  }

  # Persistence tests
  glht_low <- glht(k, linfct = "mines_diff + lag_diff + lag_diff2 = 0")
  tests_med <- k$coefficients %>% purrr::keep(grepl("medium:", names(.), fixed = TRUE)) %>% names
  tests_high <- k$coefficients %>% purrr::keep(grepl("high:", names(.), fixed = TRUE)) %>% names
  if(length(tests_med) != 0 & length(tests_high) != 0){
    hyp_test_persistent_med <- paste0("mines_diff + ", paste0(tests_med, collapse = " + "), " = 0")
    glht_med <- glht(k, linfct = hyp_test_persistent_med) %>% print
    hyp_test_persistent_high <- paste0("mines_diff + lag_diff + lag_diff2 + ", paste0(tests_high, collapse = " + "), " = 0")
    glht_high <- glht(k, linfct = hyp_test_persistent_high) %>% print
    glht_persistent <- c(glht_persistent, list(glht_low), list(glht_med), list(glht_high))
    persistence_tests <- c(persistence_tests, hyp_test_persistent_med, hyp_test_persistent_high)
  }else{
    glht_persistent <- c(glht_persistent, list(glht_low))
  }
}

rename_fun <- function(name_list){
  new <- lapply(name_list, function(x) gsub("discrete|interpol_|mean_", "", x)) %>% 
    unlist
  return(new)}


options(modelsummary_format_numeric_latex = "plain")


###############################################################################
###############################################################################
#### SUPPLEMENTARY TABLE S36
glht_contemp %>% 
  modelsummary(stars= TRUE, statistic = c("std.error", "p.value"), 
               coef_rename = rename_fun, output = "latex")
###############################################################################
###############################################################################



###############################################################################
###############################################################################
#### SUPPLEMENTARY TABLE S37
glht_persistent %>% 
  modelsummary(stars= TRUE, statistic = c("std.error", "p.value"), 
               coef_rename = rename_fun, output = "latex")
###############################################################################
###############################################################################

```



## Calculation of Total Employment Losses
```{r}

#### Data
allcomp_final <- allcomp_final %>% 
    mutate(pos_lag_diff = ifelse(lag_diff >= 0, 1, 0),
           pos_lag_diff2 = ifelse(lag_diff2 >= 0, 1, 0),
           neg_lag_diff = ifelse(lag_diff < 0, 1, 0),
           neg_lag_diff2 = ifelse(lag_diff2 < 0, 1, 0))

FE_diffuer <- as.formula("diff_uer ~ mines_diff + lag_diff + lag_diff2 + diff_log_realgdp_pc | fips + year")
model_mines <- feols(FE_diffuer, allcomp_final, se = "twoway")
model_9_both = feols(diff_uer ~ neg_diff:mines_diff + neg_lag_diff:lag_diff + neg_lag_diff2:lag_diff2 + pos_diff:mines_diff + pos_lag_diff:lag_diff + pos_lag_diff2:lag_diff2 +  diff_log_realgdp_pc | fips + year, allcomp_final, se = 'twoway')

### Absolute coal job loss numbers
coef_all <- model_mines$coefficients[1]/100 %>% unname
coef_neg <- model_9_both$coefficients['neg_diff:mines_diff']/100 %>% unname
coef_pos <- model_9_both$coefficients['mines_diff:pos_diff']/100 %>% unname

# Calculation of job loss estimates per county
job_loss_ests <- allcomp_final %>% 
  select(fips, year, mines_diff, employed, unemployed, labour_force, neg_diff, pos_diff) %>% 
  mutate(ue_effect_neg = ifelse(sign(mines_diff) == -1, labour_force*coef_all*mines_diff, 0), 
         ue_effect_pos = ifelse(sign(mines_diff) == 1, labour_force*coef_all*mines_diff, 0), 
         asymm_effect_neg = ifelse(sign(mines_diff) == -1, labour_force*coef_neg*mines_diff, 0),
         asymm_effect_pos = ifelse(sign(mines_diff) == 1, labour_force*coef_pos*mines_diff, 0),
         ue_effect_net = ue_effect_neg + ue_effect_pos,
         asymm_effect_net = asymm_effect_neg + asymm_effect_pos,
         ue_effect_neg_single = ifelse(sign(mines_diff) == -1, labour_force*coef_all*sign(mines_diff), 0), 
         ue_effect_pos_single = ifelse(sign(mines_diff) == 1, labour_force*coef_all, 0), 
         asymm_effect_neg_single = ifelse(sign(mines_diff) == -1, labour_force*coef_neg*sign(mines_diff), 0),
         asymm_effect_pos_single = ifelse(sign(mines_diff) == 1, labour_force*coef_pos, 0)) 

total_absolute <- job_loss_ests %>% 
  group_by(year) %>% 
  summarise(across(c(mines_diff, ue_effect_neg, ue_effect_pos, ue_effect_net,  asymm_effect_neg, asymm_effect_pos, asymm_effect_net), ~sum(., na.rm = TRUE))) %>% 
  ungroup


###############################################################################
###############################################################################
#### SUPPLEMENTARY TABLE S45
# Total job loss estimates on annual basis
total_absolute %>% 
  mutate(across(ue_effect_neg:asymm_effect_net, ~round(., digits = -2))) %>% 
  kable(format = "latex")

total_absolute %>% 
  summarise(across(mines_diff:asymm_effect_net, ~round(sum(., na.rm = TRUE), digits = -2))) %>% 
  kable(format = "latex")

###############################################################################
###############################################################################



###############################################################################
###############################################################################
#### SUPPLEMENTARY FIGURE S7
# Calculation of job loss estimates per county
job_loss_ests %>% 
  select(fips, ue_effect_neg, ue_effect_pos, asymm_effect_neg, asymm_effect_pos) %>% 
  pivot_longer(!fips) %>% 
  mutate(grouping = ifelse(grepl( "asymm", name), "Asymmetric Effect", "Absolute Effect"),
         Key = case_when(name == "ue_effect_neg" ~ "Closure(s)", 
                                name == "ue_effect_pos" ~ "Opening(s)", 
                                name == "asymm_effect_neg" ~ "Closure(s) - Asymmetric Effect", 
                                name == "asymm_effect_pos" ~ "Opening(s) - Asymmetric Effect"),
         Key = factor(Key, levels = c("Closure(s)",  "Opening(s)", "Closure(s) - Asymmetric Effect", "Opening(s) - Asymmetric Effect"))) %>% 
  filter(value != 0) %>% 
  ggplot() +
  geom_histogram(aes(x = value, fill = Key), bins = 100, alpha = 0.9) +
  geom_vline(aes(xintercept = mean(value) + sd(value)), linetype = "dotted") +
  geom_vline(aes(xintercept = mean(value) - sd(value)), linetype = "dotted") +
  facet_wrap(~grouping, ncol = 1) +
  theme_minimal() +
  theme(legend.position = "bottom", legend.title = element_blank()) +
  guides(fill = guide_legend(ncol = 2)) +
  labs(x = "Change in Number of Persons Unemployed", y = "Number of Observations") +
  scale_fill_brewer(palette = "Set1", direction = -1)

ggsave("output/supp_fig_s7.jpg", width = 10, height = 7, units = "in")

###############################################################################
###############################################################################


###############################################################################
###############################################################################
#### SUPPLEMENTARY FIGURE S6

# Calculation of job loss estimates per county for a single mine closure
job_loss_ests %>% 
  select(fips, contains("single")) %>% 
  pivot_longer(!fips) %>% 
  mutate(grouping = ifelse(grepl( "asymm", name), "Asymmetric Effect", "Absolute Effect"),
         Key = case_when(name == "ue_effect_neg_single" ~ "Single Closure",
                         name == "ue_effect_pos_single" ~ "Single Opening",
                         name == "asymm_effect_neg_single" ~ "Single Closure - Asymmetric Effect", 
                         name == "asymm_effect_pos_single" ~ "Single Opening - Asymmetric Effect"),
         Key = factor(Key, levels = c("Single Opening", "Single Closure",  "Single Opening - Asymmetric Effect", "Single Closure - Asymmetric Effect"))) %>% 
  filter(value != 0) %>% 
  ggplot() +
  geom_histogram(aes(x = value, fill = Key), bins = 100) +
  geom_vline(aes(xintercept = mean(value) + sd(value)), linetype = "dotted") +
  geom_vline(aes(xintercept = mean(value) - sd(value)), linetype = "dotted") +
  facet_wrap(~grouping, ncol = 1) +
  theme_minimal() +
  theme(legend.position = "bottom", legend.title = element_blank()) +
  guides(fill = guide_legend(nrow = 1)) +
  labs(x = "Change in Number of Persons Unemployed", y = "Number of Observations") + 
  scale_fill_brewer(palette = "Set2")

ggsave("output/supp_fig_s6.jpg", width = 10, height = 7, units = "in")
###############################################################################
###############################################################################


summary_stats <- job_loss_ests %>% 
  select(fips, contains("effect_")) %>% 
  mutate(across(everything(), ~ifelse(. == 0, NA, .))) %>% 
  mutate(across(contains("pos"), ~.*-1))

###############################################################################
###############################################################################
#### SUPPLEMENTARY TABLE S46
summary_stats %>% 
  select(!contains("asymm") & !contains("net")) %>% 
  data.frame %>% 
  stargazer(type = "latex",
            covariate.labels = c("Detected Effect of Closure(s)",
                                 "Detected Effect of Opening(s)",
                                 "Detected Effect of Single Closure",
                                 "Detected Effect of Single Opening"),
            title = "Detected Treatment Effects", digits = 0)

###############################################################################
###############################################################################

###############################################################################
###############################################################################
#### SUPPLEMENTARY TABLE S47
summary_stats %>% 
    select(contains("asymm") & !contains("net")) %>% 
    data.frame %>% 
    stargazer(type = "latex",
    covariate.labels = c("Detected Effect of Closure(s)",
            "Detected Effect of Opening(s)",
            "Detected Effect of Single Closure",
            "Detected Effect of Single Opening"),
            title = "Detected Treatment Effects using Asymmetric Treatment Coefficients", digits = 0)
###############################################################################
###############################################################################

```


## Linear Hypothesis Tests of Contemporaneous and Persistent Effects
```{r}

###############################################################################
###############################################################################
#### SUPPLEMENTARY TABLE S12

model_mines <- feols(FE_diffuer, allcomp_final, se = 'twoway')
  
model_neg= feols(diff_uer ~ mines_diff + neg_diff:mines_diff + 
                     lag_diff + neg_lag_diff:lag_diff +
                     lag_diff2 + neg_lag_diff2:lag_diff2 + 
                     diff_log_realgdp_pc | 
                     fips + year, allcomp_final, se = 'twoway')
  
model_pos = feols(diff_uer ~ mines_diff + pos_diff:mines_diff + 
                      lag_diff + pos_lag_diff:lag_diff + 
                      lag_diff2 + pos_lag_diff2:lag_diff2 + 
                      diff_log_realgdp_pc | 
                      fips + year, allcomp_final, se = 'twoway')
  
model_list <- list()
hyps <- data.frame()
for(k in c("mines", "neg", "pos")){
    temp_mod <- eval(parse(text = paste0("model_", k)))
    temp_names <- names(temp_mod$coefficients)[!(names(temp_mod$coefficients) == "diff_log_realgdp_pc")]
    coef_ht = temp_names[!grepl("lag", temp_names)] %>% paste(., collapse = " + ") %>% paste(., " = 0") 
    persistence_ht = temp_names %>% paste(., collapse = " + ") %>% paste(., " = 0") 
    
    coef_test = glht(temp_mod, linfct = coef_ht)
    persistence_test = glht(temp_mod, linfct = persistence_ht)
    print(coef_test)
    print(persistence_test)
    
    model_list <- c(model_list, list(coef_test), list(persistence_test))
    hyps <- rbind(hyps, 
                  c("Contemporaneous Effect", coef_ht), 
                  c("SE", NA),
                  c("p-value", NA),
                  c("Persistent Effect", persistence_ht),
                  c("SE", NA),
                  c("p-value", NA))
  }
  
rename_vector <- c("","","","","","") 
colnames(hyps) <- c("Test", "Null Hypothesis")
hyps <- hyps %>% 
    mutate(test = gsub("mines_diff ", "Beta_{1} ", `Null Hypothesis`),
           test = gsub(' lag_diff ', " Beta_{2} ", test),
           test = gsub(' lag_diff2 ', " Beta_{3} ", test),
           test = gsub("mines_diff:neg_diff", "Beta_{4}", test),
           test = gsub("lag_diff:neg_lag_diff", "Beta_{5}", test),
           test = gsub("lag_diff2:neg_lag_diff2", "Beta_{6}", test),
           test = gsub("mines_diff:pos_diff", "Beta_{7}", test),
           test = gsub("lag_diff:pos_lag_diff", "Beta_{8}", test),
           test = gsub("lag_diff2:pos_lag_diff2", "Beta_{9}", test)) %>% 
    select(-`Null Hypothesis`) %>% 
    rename(`Null Hypothesis` = test)
attr(hyps, 'position') <- c(1, 2)
model_list %>% modelsummary(stars= TRUE, statistic = c("std.error", "p.value"), coef_rename =  rename_vector, add_columns = hyps, type = "latex") %>% print



###############################################################################
###############################################################################


```



## Renewable Energy Investments: Evaluation the potential of the Inflation Reduction Act
```{r}

###############################################################################
###############################################################################
#### SUPPLEMENTARY TABLE S48

ree_model_main = feols(diff_uer ~ mines_diff + lag_diff + lag_diff2 + mines_diff:REE_bin_top90 +
                             lag_diff:l(REE_bin_top90,1) + lag_diff2:l(REE_bin_top90,2) +  REE_bin_top90 + l(REE_bin_top90,1) + l(REE_bin_top90,2) + diff_log_realgdp_pc | fips + year, allcomp, panel.id = ~fips+year,  se = 'twoway')

ree_model_test = feols(diff_uer ~ mines_diff + lag_diff + lag_diff2 + mines_diff:REE_inv_scaled_realgdp +
                             lag_diff:l(REE_inv_scaled_realgdp, 1) + lag_diff2:l(REE_inv_scaled_realgdp, 1) +  REE_inv_scaled_realgdp + l(REE_inv_scaled_realgdp, 1) + l(REE_inv_scaled_realgdp, 1) + diff_log_realgdp_pc | fips + year, test, panel.id = ~fips+year,  se = 'twoway')


etable("REE Model Main" = ree_model_main,
       "REE Model CC" = feols(diff_uer ~ mines_diff + lag_diff + lag_diff2 + mines_diff:REE_bin_top90 +
                             lag_diff:l(REE_bin_top90,1) + lag_diff2:l(REE_bin_top90,2) +  REE_bin_top90 + l(REE_bin_top90,1) + l(REE_bin_top90,2) + diff_log_realgdp_pc | fips + year, allcomp_cc, panel.id = ~fips+year, se = 'twoway'), signifCode = c(`***` = 0.001, `**` = 0.01, `*` = 0.05, . = 0.1), tex = TRUE)

###############################################################################
###############################################################################

###############################################################################
###############################################################################
#### SUPPLEMENTARY TABLE S49

etable(feols(diff_uer ~ lag_diff2 + diff_log_realgdp_pc | fips + year, allcomp, panel.id = ~fips+year,se = 'twoway'),
       feols(diff_uer ~ lag_diff2 + lag_diff2:l(REE_bin_top90, 1) + diff_log_realgdp_pc | fips + year, allcomp, panel.id = ~fips+year,se = 'twoway'),
       feols(diff_uer ~ lag_diff2 + lag_diff2:l(REE_bin_top90, 2) + diff_log_realgdp_pc | fips + year, allcomp, panel.id = ~fips+year,se = 'twoway'),
       feols(diff_uer ~ lag_diff2 + lag_diff2:l(REE_bin_top90, 2) + lag_diff2:l(REE_bin_top90, 1) + diff_log_realgdp_pc | fips + year, allcomp, panel.id = ~fips+year,se = 'twoway'), signifCode = c(`***` = 0.001, `**` = 0.01, `*` = 0.05, . = 0.1))

###############################################################################
###############################################################################

```


## PHTT: Replicate regressions incorporating REE interactions

Run on principal regressions with binary mine closure indicator incorporating USDA REE investment interaction.

Note: Interaction variables created above via static multiplication of REE binary closure, and lag of binary closure variables. This could potentially pose an issue with SE?

```{r phtt with REE}

# Incorporating interaction between REE investments and whether there was a 
# mine closure in that year.
library(phtt)

allcomp <- allcomp %>% 
  arrange(fips, year) %>%
  group_by(fips) %>% mutate(lag_ree = lag(REE_bin_top90,1), 
                            lag_ree2 = lag(REE_bin_top90, 2)) %>%
  ungroup


# Create matrices of relevant variables
dep_diff_uer <- c_mat(allcomp$diff_uer)
ind_mines_diff <- c_mat(allcomp$mines_diff)
ind_lag_diff <- c_mat(allcomp$lag_diff)
ind_lag_diff2 <- c_mat(allcomp$lag_diff2)
ind_difflogrealgdppc <- c_mat(allcomp$diff_log_realgdp_pc)
allcomp$intREE = allcomp$REE_bin_top90*allcomp$mines_diff
allcomp$intREElag = allcomp$lag_ree*allcomp$lag_diff
allcomp$intREElag2 = allcomp$lag_ree2*allcomp$lag_diff2

test_REE_KSS <- KSS(dep_diff_uer ~  -1 + ind_mines_diff + ind_lag_diff + ind_lag_diff2 + c_mat(allcomp$REE_bin_top90) + c_mat(allcomp$lag_ree) + c_mat(allcomp$lag_ree2) + c_mat(allcomp$intREE) + c_mat(allcomp$intREElag) + c_mat(allcomp$intREElag2)+ 
                    ind_difflogrealgdppc, 
                    additive.effects = "twoways", factor.dim = 0)

checkSpecif(test_REE_KSS, level = 0.001)
# Rejects null of cross-sectional independence

################################################################################
################################################################################
### SUPPLEMENTARY TABLE S50

reebin1_KSS <- KSS(dep_diff_uer ~  -1 + ind_mines_diff + ind_lag_diff + ind_lag_diff2 + c_mat(allcomp$REE_bin_top90) + c_mat(allcomp$lag_ree) + c_mat(allcomp$lag_ree2) + c_mat(allcomp$intREE) + c_mat(allcomp$intREElag) + c_mat(allcomp$intREElag2)+ 
                    ind_difflogrealgdppc, 
                    additive.effects = "twoways", factor.dim = 1)

summary(reebin1_KSS)

reebin2_KSS <- KSS(dep_diff_uer ~  -1 + ind_mines_diff + ind_lag_diff + ind_lag_diff2 + c_mat(allcomp$REE_bin_top90) + c_mat(allcomp$lag_ree) + c_mat(allcomp$lag_ree2) + c_mat(allcomp$intREE) + c_mat(allcomp$intREElag) + c_mat(allcomp$intREElag2)+ 
                    ind_difflogrealgdppc, 
                    additive.effects = "twoways", factor.dim = 2)

summary(reebin2_KSS)
################################################################################
################################################################################


```


## Panel Error Correction Models
```{r}

# using fixest ------------------------------------------------------------

allcomp %>% 
  select(year, fips, uer, active_mines, log_realgdp_pc) %>% 
  mutate(uer_lag1 = lag(uer, 1),
         uer_lag2 = lag(uer, 2),
         mines_lag1 = lag(active_mines, 1),
         mines_lag2 = lag(active_mines, 2),
         duer = uer - lag(uer, 1),
         dmines = active_mines - lag(active_mines, 1),
         dgdp = log_realgdp_pc - lag(log_realgdp_pc, 1), 
         .by = fips) %>% 
  drop_na() -> panel_ecm_data

# Estimate the ECM
ecm_model <- feols(duer ~ uer_lag1 + dmines + mines_lag1 + mines_lag2 + dgdp | fips + year, data = panel_ecm_data)


###############################################################################
###############################################################################
#### SUPPLEMENTARY TABLE S44
# Display the model summary
summary(ecm_model) %>% etable(tex = TRUE)

###############################################################################
###############################################################################

'Coefficient Interpretations

Lagged Dependent Variable (uer_lag1) Interpretation:

The coefficient of uer_lag1 is -0.252678, which is highly significant (p-value < 2.2e-16).
This negative coefficient indicates that approximately 25.27% of the deviation from the long-run equilibrium is corrected in each period. This suggests a fairly rapid adjustment towards equilibrium when there is a deviation.

Differenced Independent Variable (dmines) Interpretation:

The coefficient of dmines is -0.066292, which is highly significant (p-value = 4.8601e-14).
This negative coefficient indicates that a one-unit increase in the change of mines (mines) leads to a 0.0663 unit decrease in the change of uer (uer) in the short run. Thus, increases in mines are associated with short-run decreases in uer.

First Lag of Independent Variable (mines_lag1) Interpretation:

The coefficient of mines_lag1 is -0.025017, which is significant (p-value = 3.9057e-04).
This negative coefficient indicates that the first lag of mines has a negative long-run effect on uer. Specifically, a one-unit increase in mines from the previous period (t-1) is associated with a 0.025 unit decrease in uer in the current period.

Second Lag of Independent Variable (mines_lag2) Interpretation:

The coefficient of mines_lag2 is 0.031655, which is significant (p-value = 2.7527e-06).
This positive coefficient indicates that the second lag of mines has a positive long-run effect on uer. Specifically, a one-unit increase in mines from two periods ago (t-2) is associated with a 0.032 unit increase in uer in the current period.


Summary
Speed of Adjustment: The uer_lag1 coefficient of -0.252678 indicates that about 25.27% of any deviation from the long-run equilibrium is corrected each period.
Short-Run Dynamics:
dmines: A negative and significant coefficient (-0.066292) suggests that increases in mines reduce uer in the short run.
Long-Run Dynamics:
mines_lag1: A significant negative coefficient (-0.025017) indicates a negative long-run effect of mines lagged by one period on uer.
mines_lag2: A significant positive coefficient (0.031655) indicates a positive long-run effect of mines lagged by two periods on uer.



Combined Interpretation
Immediate Impact (Short-Run):

dmines: The immediate effect of a change in mining activities is to reduce the unemployment rate. This could be due to the direct creation of jobs and increased economic activities resulting from new mining projects or expansions.
Short-Term Lagged Effect:

mines_lag1: The positive effects of mining activities persist into the next period, continuing to reduce the unemployment rate. This suggests that the benefits of job creation and economic activity do not dissipate immediately but last into the near future.
Long-Term Lagged Effect:

mines_lag2: After two periods, the impact of increased mining activity reverses, leading to an increase in the unemployment rate. This could be due to several reasons:
Economic Adjustment: The initial boost from mining may lead to eventual layoffs or reduced hiring once initial projects are completed.
Environmental and Social Costs: Over time, negative externalities such as environmental degradation or health impacts may become apparent, reducing the long-term sustainability of the initial economic benefits.
Resource Depletion: Intensive mining activity might lead to resource depletion, which could negatively impact future mining prospects and related employment.
Relevance and Implications
Policy Implications:

Short-Term Benefits: Policymakers might leverage mining activities to achieve immediate reductions in unemployment, especially in regions with high unemployment rates.
Sustainability Concerns: Long-term planning must consider the potential adverse effects after the initial benefits fade. This includes addressing environmental concerns and ensuring that economic benefits are sustainable.
Diversification Strategies: To mitigate long-term negative effects, strategies to diversify the local economy and reduce dependency on mining might be necessary.
Economic Planning:

Job Creation: Short-term policies could focus on maximizing job creation and economic activities associated with new mining projects.
Long-Term Stability: Long-term economic policies should aim to address potential negative impacts and create a more balanced economic environment that does not solely rely on mining.
Conclusion
The coefficients for dmines, mines_lag1, and mines_lag2 provide a nuanced picture of how mining activities impact the unemployment rate over time. While mining activities have an immediate and short-term positive impact by reducing unemployment, there are potential negative long-term consequences that must be managed to ensure sustainable economic development.
'


# Pedroni Cointegration Test -----------------------------------------------------------------

library(pco)

new_ar <- array(dim = c(panel_ecm_data$year %>% unique %>% length,
                        panel_ecm_data$fips %>% unique %>% length,
                        5))
vars_pco <- c("duer","dmines","mines_lag1","mines_lag2","dgdp")

for(i in 1:length(vars_pco)){
  # i = 1
  panel_ecm_data %>% 
    select(year, fips, all_of(vars_pco[i])) %>% 
    arrange(year) %>% 
    pivot_wider(values_from = all_of(vars_pco[i]), names_from = fips) %>% 
    select(-year) %>% 
    as.matrix() -> to_be_added
  
  new_ar[,,i] <- to_be_added
}

# This is the pedroni test for cointegration (Pedroni 1999)
# these tests are described in Table 1 of the paper
# Null is no cointegration - reject for cointegration

# Mark and Sul in the paper use the "panel t-statistic" - this is probably tpanelpar    
# but why they choose that one is unclear
# we can plug the "standardised" column into a pnorm() and use the value for option "q"


pedroni_result <- pedroni99m(new_ar)


# see also Pedroni: 
# Under the alternative hypothesis, the panel variance statistic
# diverges to positive infinity, and consequently the right tail of the normal
# distribution is used to reject the null hypothesis. Consequently, for the panel
# variance statistic, large positive values imply that the null of no cointegration
# is rejected. For each of the other six test statistics, these diverge to
# negative infinity under the alternative hypothesis, and consequently the left
# tail of the normal distribution is used to reject the null hypothesis. Thus, for
# any of these latter tests, large negative values imply that the null of no
# cointegration is rejected.

# meaning: large positive values in tpanelvar --> reject null of no-cointegration
# meaning: if you have negative values, then 

# get the p-value of the test
pnorm(pedroni_result$STATISTIC[4,2])

# this is the only one we find evidence for cointegration for
pnorm(pedroni_result$STATISTIC[4,1])

###############################################################################
###############################################################################
#### SUPPLEMENTARY TABLE S43

pedroni_result$STATISTIC[1:4,] %>% 
  kableExtra::kable() %>%
  kableExtra::kable_styling()
###############################################################################
###############################################################################



```

